Predictions From Day 0 Community Structures

### 2016-07-15 code/HumanCdGF_microbiota_predict.Rmd
add variance and cfu by day plots

```{r, echo=FALSE}
Day_Euth_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_Euth_cdiff_cfu')
Day_Euth_cdiff_cfu_rf$plot
```
% Variance explained `r abs(Day_Euth_cdiff_cfu_rf$rf$rsq[length(Day_Euth_cdiff_cfu_rf$rf$rsq)]*100)`

```{r, echo=FALSE}
Day_Euth_cdiff_cfu_rf$rf

@@

@@

@@

```{r,echo=FALSE}
#rf to predict 
Day_1_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_1_cdiff_cfu')
Day_1_cdiff_cfu_rf$plot
```
```{r, echo=FALSE}
Day_1_cdiff_cfu_rf$rf
````

# Day 2 C. difficile CFU
```{r, echo=FALSE}
Day_2_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_2_cdiff_cfu')
Day_2_cdiff_cfu_rf$plot
````
```{r, echo=FALSE}
Day_2_cdiff_cfu_rf$rf
````

# Day 3 C. difficile CFU
```{r, echo=FALSE}
Day_3_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_3_cdiff_cfu')
Day_3_cdiff_cfu_rf$plot
````
```{r, echo=FALSE}
Day_3_cdiff_cfu_rf$rf
````

# Day 4 C. difficile CFU
```{r, echo=FALSE}
Day_4_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_4_cdiff_cfu')
Day_4_cdiff_cfu_rf$plot
````
```{r, echo=FALSE}
Day_4_cdiff_cfu_rf$rf
````

# Day 5 C. difficile CFU
```{r, echo=FALSE}
Day_5_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_5_cdiff_cfu')
Day_5_cdiff_cfu_rf$plot
````
```{r, echo=FALSE}
Day_5_cdiff_cfu_rf$rf
````

# Day 6 C. difficile CFU
```{r, echo=FALSE}
Day_6_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_6_cdiff_cfu')
Day_6_cdiff_cfu_rf$plot
````
```{r, echo=FALSE}
Day_6_cdiff_cfu_rf$rf
````

# Day 7 C. difficile CFU
```{r, echo=FALSE}
Day_7_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_7_cdiff_cfu')
Day_7_cdiff_cfu_rf$plot
```
```{r, echo=FALSE}
Day_7_cdiff_cfu_rf$rf
```

# Day 8 C. difficile CFU
```{r, echo=FALSE}
Day_8_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_8_cdiff_cfu')
Day_8_cdiff_cfu_rf$plot
```
```{r, echo=FALSE}
Day_8_cdiff_cfu_rf$rf
```

# Day 9 C. difficile CFU
```{r, echo=FALSE}
Day_9_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_9_cdiff_cfu')
Day_9_cdiff_cfu_rf$plot
```
```{r, echo=FALSE}
Day_9_cdiff_cfu_rf$rf
```

# Day 10 C. difficile CFU
```{r, echo=FALSE}
Day_10_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_10_cdiff_cfu')
Day_10_cdiff_cfu_rf$plot
```
```{r, echo=FALSE}
Day_10_cdiff_cfu_rf$rf
```

Predicting CFU from day 1 to 10 based on Day 0 community
There seems a flucuation in the % variance explained, from none to > 20%
There s

```{r knitr::kable, echo=FALSE}
var_by_day <- data.frame(Day=c(1:10),
                         Percent_Variance_Explained=c(21.86,43.56,4.810,-4.12,2.740,67.63,9.390,33.29,61.19,-6.21),
                         Mean_of_squared_residuals=c(5.59e15,3.3e15,6.87e16,5.62e16,4.23e15,7.43e15,2.95e16,3.84e15,9.65e15,1.5e17))
knitr::kable(var_by_day)
```

>>>>

```{r, echo=FALSE}
Day_Euth_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_Euth_cdiff_cfu')
Day_Euth_cdiff_cfu_rf$plot
```

% Variance explained `r Day_Euth_cdiff_cfu_rf$rf$rsq[length(Day_Euth_cdiff_cfu_rf$rf$rsq)]*100`

***

@@

% Variance explained `r Day_10_cdiff_cfu_rf$rf$rsq[length(Day_10_cdiff_cfu_rf$rf$rsq)]*100`

@@

***

@@

```{r,echo=FALSE}
#rf to predict 
Day_1_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_1_cdiff_cfu')
Day_1_cdiff_cfu_rf$plot
```

% Variance explained `r Day_1_cdiff_cfu_rf$rf$rsq[length(Day_1_cdiff_cfu_rf$rf$rsq)]*100`

# Day 2 C. difficile CFU
```{r, echo=FALSE}
Day_2_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_2_cdiff_cfu')
Day_2_cdiff_cfu_rf$plot
```

% Variance explained `r Day_2_cdiff_cfu_rf$rf$rsq[length(Day_2_cdiff_cfu_rf$rf$rsq)]*100`

# Day 3 C. difficile CFU
```{r, echo=FALSE}
Day_3_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_3_cdiff_cfu')
Day_3_cdiff_cfu_rf$plot
```

% Variance explained `r Day_3_cdiff_cfu_rf$rf$rsq[length(Day_3_cdiff_cfu_rf$rf$rsq)]*100`

# Day 4 C. difficile CFU
```{r, echo=FALSE}
Day_4_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_4_cdiff_cfu')
Day_4_cdiff_cfu_rf$plot
```

% Variance explained `r Day_4_cdiff_cfu_rf$rf$rsq[length(Day_4_cdiff_cfu_rf$rf$rsq)]*100`

# Day 5 C. difficile CFU
```{r, echo=FALSE}
Day_5_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_5_cdiff_cfu')
Day_5_cdiff_cfu_rf$plot
```

% Variance explained `r Day_5_cdiff_cfu_rf$rf$rsq[length(Day_5_cdiff_cfu_rf$rf$rsq)]*100`

# Day 6 C. difficile CFU
```{r, echo=FALSE}
Day_6_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_6_cdiff_cfu')
Day_6_cdiff_cfu_rf$plot
```

% Variance explained `r Day_6_cdiff_cfu_rf$rf$rsq[length(Day_6_cdiff_cfu_rf$rf$rsq)]*100`

# Day 7 C. difficile CFU
```{r, echo=FALSE}
Day_7_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_7_cdiff_cfu')
Day_7_cdiff_cfu_rf$plot
```

% Variance explained `r Day_7_cdiff_cfu_rf$rf$rsq[length(Day_7_cdiff_cfu_rf$rf$rsq)]*100`

# Day 8 C. difficile CFU
```{r, echo=FALSE}
Day_8_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_8_cdiff_cfu')
Day_8_cdiff_cfu_rf$plot
```

% Variance explained `r Day_8_cdiff_cfu_rf$rf$rsq[length(Day_8_cdiff_cfu_rf$rf$rsq)]*100`

# Day 9 C. difficile CFU
```{r, echo=FALSE}
Day_9_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_9_cdiff_cfu')
Day_9_cdiff_cfu_rf$plot
```

% Variance explained `r Day_9_cdiff_cfu_rf$rf$rsq[length(Day_9_cdiff_cfu_rf$rf$rsq)]*100`

# Day 10 C. difficile CFU
```{r, echo=FALSE}
Day_10_cdiff_cfu_rf <- run_rf_on(Predict_df,'Day_10_cdiff_cfu')
Day_10_cdiff_cfu_rf$plot
```

% Variance explained `r Day_10_cdiff_cfu_rf$rf$rsq[length(Day_10_cdiff_cfu_rf$rf$rsq)]*100`

Predicting CFU from day 1 to 10 based on Day 0 community

There seems a flucuation in the % variance explained, which seems to coincide with the flutuations in cdiff cfu

```{r knitr::kable, echo=FALSE, warning=F, message=F}
var_by_day <- data.frame(Day=c(1:10),Percent_Variance_Explained=NA)
cdiff_cfu <- vector()
for (a in 1:10){
          var_by_day$Percent_Variance_Explained[a] <- eval(parse(text = paste('Day_', a, '_cdiff_cfu_rf$rf$rsq[length(Day_', a, '_cdiff_cfu_rf$rf$rsq)]*100', sep='')))
          cdiff_cfu <- c(cdiff_cfu,paste('Day_', a, '_cdiff_cfu', sep=''))
     }

knitr::kable(var_by_day)
plot(var_by_day, type='n', xlab='Day',ylab='Percent Var Explained')
lines(var_by_day$Day, var_by_day$Percent_Variance_Explained)

cfu_plot <- cbind(Mouse = paste(Predict_df$human_source,Predict_df$mouse_eartag, sep='_'),Predict_df[, cdiff_cfu])
names(cfu_plot) <- c('Mouse', c(1:10))
cfu_plot <- reshape2::melt(cfu_plot, by='Mouse')

ggplot(data=cfu_plot, aes(x=variable, y=value, group=Mouse)) + geom_line(aes(color=Mouse)) + geom_point() + scale_y_log10() +
     theme_classic() + theme(legend.position='none') + labs(title='C. Difficile CFU by mouse',x='Day',y='CFU')
```
